---
title: "Final Project"
author: "Takashi Takizawa"
date: "2017/4/8"
output: html_document
---

#Table of contents
1. Data cleaning & preparation 
2. KNN model
3. SVM model
4. ANN model
5. Model accuracy
6. Ensemble prediction


#1. Data cleaning & preparation 

Data cleaning
```{r setup, include=FALSE}
speed <- read.csv("Speed Dating Data.csv")
speed$condtn <- as.factor(speed$condtn)
speed$gender <- as.factor(speed$gender)
#speed$match <- as.factor(speed$match)
speed$field_cd <- as.factor(speed$field_cd)
levels(speed$field_cd) <- c("Law","Math","SocScie/Psych", "MedSci", "Engineering", "English", "History", "Business", "Education", "Bio","SocialWork","Undergrad", "PoliSci", "Film","FineArts","Lang","Architecture","Other")
speed$race <- as.factor(speed$race)
speed$goal <- as.factor(speed$goal)
levels(speed$goal) <- c("FunNightOut", "MeetNewPpl", "GetADate","SRSRelationship", "ToSayIDidIt","Other")

speed$date <- as.factor(speed$date)
#Don't convert to date as character
#levels(speed$date) <- c("SVRL/Week","2/Week","1/Week","2/Month", "1/Month", "SVRL/Year", "AlmostNever")

speed$go_out <- as.factor(speed$go_out)
levels(speed$go_out) <- c("SVRL/Week","2/Week","1/Week","2/Month", "1/Month", "SVRL/Year", "AlmostNever")
speed$career_c <-as.factor(speed$career_c)
levels(speed$career_c) <- c("Lawyer","Academic/Research","Psychologist","DocMed", "Engineer", "Entertainment", "Banking/Consulting", "RealEstate","IntlAffairs","Undecided","SocialWork","SpeechPath","Politics", "ProSports", "Other", "Journalism", "Architecture")
speed$race_o <-as.factor(speed$race_o) 
speed$dec_o <- as.factor(speed$dec_o)
#speed$samerace <- as.factor(speed$samerace)

sd2 <- speed
sd2 <- sd2[ , -1] #IID  
sd2 <- sd2[, -1] #ID  
sd2 <- sd2[, -2] #IDG
sd2 <- sd2[, -3] #Wave
sd2 <- sd2[, -3] #Round
sd2 <- sd2[, -3] #Position
sd2 <- sd2[, -3] #Postion1
sd2 <- sd2[, -4] #Partner 
sd2 <- sd2[, -4] #PID
sd2 <- sd2[, -26]#Field
sd2 <- sd2[, -(27:29)]#Academics
sd2 <- sd2[,-(30:32)]#Socioeconomic 
sd2 <- sd2[,-33]#Career
sd2 <- sd2[,-(59:64)]#What others look for
sd2 <- sd2[,-(70:74)]#Others perception
sd2 <- sd2[,-(81:92)]#Data gathered after intitial
sd2 <- sd2[,(1:79)]
sd2 <- sd2[,-(70:79)] #Removes Post First Date
sd2 <- sd2[,-52]#exclude expnum

sd2$mn_sat <- speed$mn_sat
sd2$mn_sat[sd2$mn_sat==""]<-NA

sdrandom <- sd2[sample(nrow(sd2), nrow(sd2)),] #Get a random sample since the data is organized by participant

sdclean <- na.omit(sdrandom) #Remove rows with NA values to create a "clean" set
```

Overview of cleaned data
```{r}
names(sdclean)
```


Create new variables to show gaps between objects and partners
```{r}
normalize<-function(x){
  return((x-min(x))/(max(x)-min(x)))}

#age difference
sdclean$age_dif<-sdclean$age - sdclean$age_o

#intelligence difference between sat score and partner's preference
x<-data.frame(lapply(sdclean[18], normalize))
sdclean$mn_sat<-as.numeric(sdclean$mn_sat)
y<-as.data.frame(lapply(sdclean[69], normalize))
z<- x-y
```

Normalize variables
```{r}
#age difference
a<-data.frame(lapply(sdclean[70], normalize))
sdclean$age_dif<-a$age_dif

#intelligence difference
b<-as.data.frame(lapply(z[1], normalize))
sdclean$intel_dif<-b$intel_o

#date frequency
sdclean$date<-as.numeric(sdclean$date)
c<-data.frame(lapply(sdclean[31], normalize))
sdclean$date_norm<-c$date

```

Delete unnecessary columns
```{r}
sdfinal <- sdclean[,c(4,6,70:72)]
str(sdfinal)
```

Create train & test data
```{r}
##Make train and test data
data_train<-sdfinal[1:1948,]
data_test<-sdfinal[1949:2436,]

#Make labels for train and test data
data_train_label<-sdfinal[1:1948,1]
data_test_label<-sdfinal[1949:2436,1]
```

#2. KNN Model: The model accuracy is XXX%
```{r}
library(class)

#Delete target variable from train data
data_train_knn<-data_train[-1]
data_test_knn<-data_test[-1]

#Develop KNN Model
knn_data_pred<-knn(train=data_train_knn, test=data_test_knn, cl=data_train_label, k=44)

#Inspect model accuracy
#library(gmodels)
#CrossTable(x=data_test_label,y=knn_data_pred,prop.chisq = FALSE)

#88.8% accuracy in the previous model run 
```


#3. SVM Model: The model accuracy is XXX%
```{r}
library(kernlab)

#Develop SVM model
data_classifier <- ksvm(match ~ ., data = data_train, kernel = "vanilladot")
svm_data_pred <- predict(data_classifier, data_test)
svm_data_pred <- ifelse(svm_data_pred>0.5, 1, 0)

#Inspect model accuracy
#table(svm_data_pred, data_test$match)
#agreement <- svm_data_pred == data_test$match
#table(agreement)
#prop.table(table(agreement))

#89.9% accuracy in the previous model run
```

#4. ANN Mode: The model accuracy is XXX%
```{r}
library(neuralnet)

#remove response from dataset
data_train_ann <- data_train[-1]

#create list of columns separated by "+" for neuralnet formula
n_train <- names(data_train_ann)
ANN_f <- as.formula(paste("match ~", paste(n_train, collapse = " + ")))

#run neuralnet
train_ann <- neuralnet(formula = ANN_f, data = data_train, lifesign = "full", hidden = 5)

#apply train_ann model to test data
model_results_ann <- compute(train_ann, data_test[-1])

#stats of match test predictions
summary(model_results_ann$net.result)

#set cut-off for match to 3rd quartile (0.2016975), just to pick something less arbitrary than 0.5
ann_predicted_match <- ifelse(model_results_ann$net.result > 0.2016975, 1, 0)

#how did we do?
#ann_output <- CrossTable(x = data_test_label, y = ann_predicted_match, 
           prop.chisq=FALSE)

#pretty awful!

```

#5. Model Accuracy
```{r}

accuracy <- function(predicted, trueval, model, hideoutput = F) {
  stopifnot(length(predicted) == length(trueval))
  result <- sum(predicted == trueval) / length(predicted)
  if (!hideoutput) {cat("Model:", model, "had", result, "accuracy\n")}
  return(result)
}

print(accuracy(svm_data_pred,data_test_label,"SVM"))
print(accuracy(knn_data_pred,data_test_label,"kNN"))
print(accuracy(ann_predicted_match,data_test_label,"ANN"))

```


#6. Create Ensemble Model
```{r}

# Convert all of the feature data to factors....
ConvertToYesNo <- function(myprediction) {
  result <- myprediction %>% as.factor()
  levels(result) <- c("no", "yes")
  result
}

library(magrittr)
library(dplyr)

# Convert each set of predictions to factors
knn_data_pred %<>% ConvertToYesNo()
svm_data_pred %<>% ConvertToYesNo()
ann_predicted_match %<>% ConvertToYesNo()

model_combined_results <- data.frame(knn_data_pred, svm_data_pred, ann_predicted_match) %>% as.tbl()

summary(model_combined_results)
str(data_test_label)

# Create the model -> Stacking with a Ctree to find out if it helps any!
library(partykit)

stacked_model <- ctree(data_test_label ~ ., data = model_combined_results) %T>% plot
#, controls = ctree_control(mincriterion = 0.99999)

```


